---
title: "Registration Report Fall 2023"
subtitle: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Office of Institutional Effectiveness and Research"
geometry: margin=1cm
output:
  pdf_document: default
  
  
---

```{r include=FALSE}
library(readxl)
library(tidyverse)
library(kableExtra)
library(stringi)
library(stringr)
library(chron)
library(zoo)
library(data.table)
library(scales)
pull <- read_excel("C://Users//jamesa-anderson//OneDrive - John A. Logan College//Documents//spring.xlsx")
count <- read_excel("C://Users//jamesa-anderson//OneDrive - John A. Logan College//Documents//spring.xlsx", 
    sheet = "head")
pull$Section<-stri_sub(pull$Course, -2)
pull$Course<-substr(pull$Course,1,nchar(pull$Course)-4)
pull$Course<-gsub("\\s+"," ",pull$Course)
pull$Division<-str_replace_all(pull$Division, c("AE$" = "Adult Education", "AH$" = "Allied Health", "AT$" = "Applied Technology", "HS$" = "Humanities and Social Science", "MB$" = "Business, Computer Science, and Math", "ND$" = "Nursing", "SC$" = "Life and Physical Science", "SI$" = "SICCM", "WD$" = "Workforce Development", "NULL" = "Independet Study"))
pull$InstructionMode<-str_replace_all(pull$InstructionMode, c("CLAS$" = "Classroom", "HYB$" = "Hybrid", "OLA$" = "On-Line Anytime", "OLS$" = "On-Line Scheduled"))
```

```{r include=FALSE}
dual <- read_excel("~/dual enrollment.xlsx")
dual$Division<-str_replace_all(dual$Division, c("AE$" = "Adult Education", "AH$" = "Allied Health", "AT$" = "Applied Technology", "HS$" = "Humanities and Social Science", "MB$" = "Business, Computer Science, and Math", "ND$" = "Nursing", "SC$" = "Life and Physical Science", "SI$" = "SICCM", "WD$" = "Workforce Development"))
dual.total<-dual %>% group_by(Division) %>% summarise('Dual Credit' = sum(Enrolled))
sum(dual$Enrolled*dual$Hours)
```
# Division Totals

```{r echo=FALSE}
todays.date<-Sys.Date()
table.1<-data.frame(length(unique(count$ID)), sum((pull$Enrolled+pull$Waitlist)*pull$CreditHours), sum((pull$Enrolled+pull$Waitlist)*pull$CreditHours)/15)
table.1<-round(table.1, digits=2)
colnames(table.1)<-c("Unduplicated Headcount", "Total Credit Hours", "FTE")
kable(table.1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Unduplicated Headcount, Total Hours, and FTE on ", todays.date, sep = " ")) %>%
  kable_styling(font_size = 7, latex_options = c("hold_position", "repeat_header"))
pull$PercentCap <-round((pull$Enrolled+pull$Waitlist)/pull$Capacity, 2)
pull$PercentCap[!is.finite(pull$PercentCap)] <- 0
average.mean<-round(mean(pull$Enrolled),0)
total.enrolled<-round(sum(pull$Enrolled+pull$Waitlist),0)
average.capacity<-round(mean(pull$Capacity),0)
total.capacity<-round(sum(pull$Capacity),0)
Total<-c("Total", scales::percent(total.enrolled/sum(pull$Capacity)), total.enrolled, average.mean, average.capacity)
division.total<-pull %>% group_by(Division) %>% summarise(AverageCap = round(mean(PercentCap, na.rm=TRUE), 2), AverageCap=scales::percent(AverageCap) , TotalEnrolment = round(sum(Enrolled)), AverageEnrollment = round(mean(Enrolled)), AverageCapacity = round(mean(Capacity)))
division.total<-rbind(division.total, Total)
division.total<-merge(division.total, dual.total, by='Division', all=TRUE)
division.total<-division.total %>% replace(is.na(.), 0)
division.total<-rbind(division.total[1:7,], division.total[9,], division.total[8,])
names(division.total)[length(names(division.total))]<-"Dual Credit"
division.total$TotalEnrolment<-as.numeric(division.total$TotalEnrolment)-as.numeric(division.total$`Dual Credit`)
row.names(division.total)<- NULL
kable(division.total, row.names = FALSE, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Division Totals on", todays.date, sep = " ")) %>%
  kable_styling(font_size = 7, latex_options = c("hold_position", "repeat_header"))
pull.ggplot<-ggplot(pull, aes(x=Division, y=mean(Enrolled)))
online<-pull %>% filter(substr(InstructionMode, 1, 1) == "O")
inperson<-pull %>% filter(substr(InstructionMode, 1, 1) != "O")
online.table<-c(mean(online$Enrolled+online$Waitlist), mean(online$Capacity), mean((online$Enrolled+online$Waitlist))/mean(online$Capacity, na.rm=TRUE))
inperson.table<-c(mean(inperson$Enrolled+inperson$Waitlist), mean(inperson$Capacity), mean((inperson$Enrolled+inperson$Waitlist))/mean(inperson$Capacity, na.rm=TRUE))
online.table[1:2]<-round(online.table[1:2], digit=0)
inperson.table[1:2]<-round(inperson.table[1:2], digit=0)
instructionmode.table<-rbind(inperson.table, online.table)
rownames(instructionmode.table)<-c("In-Person", "Online")
colnames(instructionmode.table)<-c("Average Enrolled", "Average Capacity", "Average Percent Capacity")
instructionmode.table[,3]<-percent(instructionmode.table[,3])
kable(instructionmode.table, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Average Enrollment, Average Capacity, and Average Percent Capacity for ", todays.date, sep = " ")) %>%
  kable_styling(font_size = 7, latex_options = c("hold_position", "repeat_header"))
todays.date<-format(todays.date, format="%B %d %Y")
pull.ggplot + geom_col(fill="blue") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + labs(title="Students Enrolled in Divisions", subtitle=todays.date, x="Divisions", y="Students Enrolled in Class in Division")


```





\newpage

\begin{landscape}
\section{Adult Education}

```{r echo=FALSE, comment=NA, paged.print=TRUE, results= "asis"}
ae.table<-pull %>% filter(Division == "Adult Education") %>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled, Waitlist, Capacity, CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(ae.table)[1] > 0){ 
ae.S1<-ae.table %>% filter(Term == "S1")
ae.S2<-ae.table %>% filter(Term == "S2")
ae.S4<-ae.table %>% filter(Term == "S4")
ae.S8<-ae.table %>% filter(Term == "S8")
ae.null<-ae.table %>% filter(Term == "NULL")
ae.over<-ae.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
ae.over[is.na(ae.over)] <- 0
print(kable(ae.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Adult Education Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ae.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Adult Education for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ae.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Adult Education for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ae.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Adult Education for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ae.S8, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Adult Education for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ae.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Adult Education for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")}
```



\end{landscape}

\newpage


\begin{landscape}
\section{Allied Health}
```{r echo=FALSE, comment=NA, paged.print=TRUE, results = "asis"}
ah.table<-pull %>% filter(Division == "Allied Health") %>% group_by(Course)  %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled,Waitlist, Capacity, CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(ah.table)[1] > 0){ 
ah.S1<-ah.table %>% filter(Term == "S1")
ah.S2<-ah.table %>% filter(Term == "S2")
ah.S4<-ah.table %>% filter(Term == "S4")
ah.S6<-ah.table %>% filter(Term == "S6")
ah.null<-ah.table %>% filter(Term == "NULL")
ah.over<-ah.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
ah.over[is.na(ah.over)] <- "0%"
print(kable(ah.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Life and Physical Science Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ah.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Allied Health for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ah.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Allied Health for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ah.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Allied Health for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ah.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Allied Health for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ah.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Allied Health for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")}
```
\end{landscape}
\newpage


\begin{landscape}
\section{Applied Technology}
```{r echo=FALSE, comment=NA, paged.print=TRUE, comment=NA, results = "asis"}
at.table<-pull %>% filter(Division == "Applied Technology") %>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled, Waitlist,Capacity, CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(at.table)[1] > 0){ 
at.S1<-at.table %>% filter(Term == "S1")
at.S2<-at.table %>% filter(Term == "S2")
at.S4<-at.table %>% filter(Term == "S4")
at.S6<-at.table %>% filter(Term == "S6")
at.null<-at.table %>% filter(Term == "NULL")
at.over<-at.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
at.over[is.na(at.over)] <- "0%"
print(kable(at.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Applied Technology Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(at.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Applied Technology for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(at.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Applied Technology for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(at.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Applied Technology for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(at.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Applied Technology for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(at.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Applied Technology for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")}
```
\end{landscape}
\newpage



\begin{landscape}
\section{Humanities and Social Science}
```{r echo=FALSE, paged.print=TRUE, comment=NA, results = "asis"}
hs.table<-pull %>% filter(Division == "Humanities and Social Science") %>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled,Waitlist, Capacity, CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(hs.table)[1] > 0){ 
hs.S1<-hs.table %>% filter(Term == "S1")
hs.S2<-hs.table %>% filter(Term == "S2")
hs.S4<-hs.table %>% filter(Term == "S4")
hs.S6<-hs.table %>% filter(Term == "S6")
hs.null<-hs.table %>% filter(Term == "NULL")
hs.over<-hs.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
hs.over[is.na(hs.over)] <- "0%"
print(kable(hs.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Humanities and SOcial Science Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(hs.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Humanities and Social Science for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(hs.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Humanities and Social Science for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(hs.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Humanities and Social Science for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(hs.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Humanities and Social Science for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(hs.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Humanities and Social Science for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")}
```
\end{landscape}
\newpage


\begin{landscape}
\section{Business, Computer Science, and Mathematics}
```{r echo=FALSE, paged.print=TRUE, comment=NA, results = "asis"}
mb.table<-pull %>% filter(Division == "Business, Computer Science, and Math") %>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled,Waitlist, Capacity, CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(mb.table)[1] > 0){ 
mb.S1<-mb.table %>% filter(Term == "S1")
mb.S2<-mb.table %>% filter(Term == "S2")
mb.S4<-mb.table %>% filter(Term == "S4")
mb.S6<-mb.table %>% filter(Term == "S6")
mb.null<-mb.table %>% filter(Term == "NULL")
mb.over<-mb.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
mb.over[is.na(mb.over)] <- "0%"
print(kable(mb.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Math and Business Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(mb.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Business, Computer Science, and Mathematics for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(mb.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Business, Computer Science, and Mathematics for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(mb.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Business, Computer Science, and Mathematics for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(mb.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Business, Computer Science, and Mathematics for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(mb.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Business, Computer Science, and Mathematics for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")} 
```
\end{landscape}
\newpage



\begin{landscape}
\section{Nursing}
```{r echo=FALSE, paged.print=TRUE, comment=NA, results = "asis"}
nu.table<-pull %>% filter(Division == "Nursing")%>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled, Waitlist,Capacity, CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(nu.table)[1] > 0){ 
nu.S1<-nu.table %>% filter(Term == "S1")
nu.S2<-nu.table %>% filter(Term == "S2")
nu.S4<-nu.table %>% filter(Term == "S4")
nu.S6<-nu.table %>% filter(Term == "S6")
nu.null<-nu.table %>% filter(Term == "NULL")
nu.over<-nu.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
nu.over[is.na(nu.over)] <- "0%"
print(kable(nu.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Nursing Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(nu.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Nursing for First Half Classes on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(nu.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Nursing for Second Half Classes on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(nu.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Nursing for Full Term Classes on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(nu.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Nursing for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(nu.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Nursing for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")}
```
\end{landscape}
\newpage


\begin{landscape}
\section{Life and Physical Science}
```{r echo=FALSE, paged.print=TRUE, comment=NA, results = "asis"}
ps.table<-pull %>% filter(Division == "Life and Physical Science") %>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled,Waitlist, Capacity,  CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(ps.table)[1] > 0){ 
ps.S1<-ps.table %>% filter(Term == "S1")
ps.S2<-ps.table %>% filter(Term == "S2")
ps.S4<-ps.table %>% filter(Term == "S4")
ps.S6<-ps.table %>% filter(Term == "S6")
ps.null<-ps.table %>% filter(Term == "NULL")
ps.over<-ps.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
ps.over[is.na(ps.over)] <- "0%"
print(kable(ps.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Life and Physical Science Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ps.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Life and Physical Science for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ps.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Life and Physical Science for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ps.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Life and Physical Science for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ps.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Life and Physical Science for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(ps.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Life and Physical Science for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")}

```
\end{landscape}
\newpage

\begin{landscape}
\section{SICCM}
```{r echo=FALSE, paged.print=TRUE, comment=NA, results = "asis"}
si.table<-pull %>% filter(Division == "SICCM") %>% group_by(Course) %>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled,Waitlist, Capacity, CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(si.table)[1] > 0){ 
si.S1<-si.table %>% filter(Term == "S1")
si.S2<-si.table %>% filter(Term == "S2")
si.S4<-si.table %>% filter(Term == "S4")
si.S6<-si.table %>% filter(Term == "S6")
si.null<-ps.table %>% filter(Term == "NULL")
si.over<-si.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
si.over[is.na(si.over)] <- "0%"
print(kable(si.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("SICCM Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(si.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("SICCM for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(si.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("SICCM for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(si.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("SICCM for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(si.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("SICCM for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(si.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("SICCM for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")}
```
\end{landscape}
\newpage

\begin{landscape}
\section{Workforce Development}
```{r echo=FALSE, paged.print=TRUE, comment=NA, results = "asis"}
wd.table<-pull %>% filter(Division == "Workforce Development") %>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled, Waitlist,Capacity,  CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(wd.table)[1] > 0){ 
wd.S1<-wd.table %>% filter(Term == "S1")
wd.S2<-wd.table %>% filter(Term == "S2")
wd.S4<-wd.table %>% filter(Term == "S4")
wd.S6<-wd.table %>% filter(Term == "S8")
wd.null<-wd.table %>% filter(Term == "NULL")
wd.over<-wd.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
wd.over[is.na(wd.over)] <- "0%"
print(kable(wd.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(wd.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(wd.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(wd.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(wd.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(wd.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")} 
```
\end{landscape}

\newpage

\begin{landscape}
\section{Independent Study}
```{r echo=FALSE, paged.print=TRUE, comment=NA, results = "asis"}
id.table<-pull %>% filter(Division == "NULL") %>% group_by(Course)%>% group_by(Course) %>% select(Course, Section, Term, InstructionMode, Instructor, ClassDay, StartDate, EndDate, Enrolled,Waitlist, Capacity,  CreditHours, PercentCap) %>% arrange(Course, Section, desc(PercentCap)) %>% mutate(PercentCap, PercentCap=scales::percent(PercentCap))
if(dim(wd.table)[1] > 0){ 
id.S1<-id.table %>% filter(Term == "S1")
id.S2<-id.table %>% filter(Term == "S2")
id.S4<-id.table %>% filter(Term == "S4")
id.S6<-id.table %>% filter(Term == "S6")
id.null<-id.table %>% filter(Term == "NULL")
id.over<-id.table %>% group_by(Course) %>% select(Course, Enrolled, Capacity, CreditHours) %>% summarise(Total=sum(Enrolled), Average=sum(Enrolled), TotalCap=sum(Capacity), TotalPercentCap=scales::percent(Total/TotalCap))
id.over[is.na(id.over)] <- "0%"
print(kable(id.over, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Independent Study Class Totals on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(id.S1, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for First Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(id.S2, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for Second Half Class on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(id.S4, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for Full Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(id.S6, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for Middle Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
print(kable(id.null, "latex", booktabs = TRUE, longtable = TRUE, caption = paste("Workforce Development for Other Term on", todays.date, sep = " ")) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")))
} else {cat("No Classes for this Division")} 
```
\end{landscape}

```{r comment=NA, include=FALSE}
library(openxlsx)
list_of_datasets <- list("Allied Health" = ah.table, "Applied Technology" = at.table, "Humanities and Social Science" = hs.table, "Math and Business" = mb.table, "Nursing" = nu.table, "Physical and Life Science" = ps.table, "SICCM" = si.table, "Workforce Development" = wd.table, "Independent Study" = id.table, "All" = pull)
#Network storage remove to write to network
write.xlsx(list_of_datasets, file=paste0("G:\\Institutional Research\\From James\\enrollment pull\\daily reports\\spring daily report ", format(Sys.Date(), "%m-%d"), ".xlsx"))
#Local Storage remove to write local
write.xlsx(list_of_datasets, file=paste0("spring daily report ", format(Sys.Date(), "%m-%d"), ".xlsx"))
```

```{r eval=FALSE, comment=NA, include=FALSE}
spring<-read.csv("G:\\Institutional Research\\From James\\enrollment pull\\falltracking.csv")
col_names <- intersect(names(pull), names(spring))
write<-merge(pull, spring, by=col_names, all.x=TRUE)
write$Today<-write$Enrolled+write$Waitlist
write<-write[,-c(11,12)]
names(write)[length(names(write))]<-todays.date
write.csv(write, file=paste0('G:\\Institutional Reseah\\From James\\enrollment pull\\spring', format(Sys.Date(),"%m-%d"), '.csv'))
```

